Paper Figure Generation

### 2022-06-22 R/PaperFigureGeneration.rmd
Created PaperFigureGeneration
- This is a dedicated R notebook for generating the figures to be used in the publication associated with the analysis.
- TODO: Need to split up figure generation chunks to account for different figure sizes.

NHF1CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)

@@

NHF1DataDirectory = file.path(deaminationDirectory, "NHF1")
NHF1SequenceAndPositionDataDirectory = file.path(NHF1DataDirectory, "sequence_and_position_analysis")
NHF1ExcisionSiteDataDirectory = file.path(NHF1DataDirectory, "excision_site_analysis")
NHF1GeneralReadSequenceDataDirectory = file.path(NHF1DataDirectory, "general_read_sequences")

arabidopsisDataDirectory = file.path(deaminationDirectory, "Arabidopsis")
arabidopsisSequenceAndPositionDataDirectory = file.path(arabidopsisDataDirectory, "sequence_and_position_analysis")
arabidopsisExcisionSiteDataDirectory = file.path(arabidopsisDataDirectory, "excision_site_analysis")

yeastDataDirectory = file.path(deaminationDirectory, "yeast")
yeastSequenceAndPositionDataDirectory = file.path(yeastDataDirectory, "sequence_and_position_analysis")
yeastExcisionSiteDataDirectory = file.path(yeastDataDirectory, "excision_site_analysis")
```

@@

```{r read_figure_2_data}
NHF1CPDMismatchDataAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllReps)) {
  NHF1CPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(CPDMismatchData)[i], repitition = "all_reps"
  ))
}
```

@@

plotTrinucleotideContext(NHF1CPDMismatchData$`1h`, includedTypes = c("C>T"),
                         title = "NHF1 CPD 1h All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(NHF1CPDMismatchData$`1h`, includedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps Mismatch Pos Frequencies")
```

```{r read_figure_3_data}
NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
for (i in seq_along(CPDMMFreqZScores)) {
  NHF1CPDMMFreqZScoresAllReps[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(CPDMMFreqZScores)[i], includedMismatches = c("C>T")
  ))
}

@@

NHF1CPDTGGSeqFreqAllReps = NHF1CPDTimepoints
for (i in seq_along(CPDTGGSeqFreq)) {
  NHF1CPDTGGSeqFreqAllReps[[i]] = fread(generateFilePath(
    directory = NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDTGGSeqFreqAllReps)[i], sequence = "TGG"
  ))
}
```

```{r figure_3}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]]["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = CPDMMFreqZScores)

@@

plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        expansionOffset = 10, showThreePrimeCutSite = TRUE,
                        showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
```

```{r figure_3_alt}
plotPositionAcrossTimepointAndReadLength(CPDMismatchData[[i]], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = CPDMMFreqZScores)

plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 12)

plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        expansionOffset = 10, showThreePrimeCutSite = TRUE,
                        showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
```

>>>>

NHF1CPDTimepoints = list(`1h` = NULL, `8h` = NULL, `24h` = NULL, `48h` = NULL)
NHF1SixFourTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
arabidopsisCPDTimepoints = list(`ZT2` = NULL, `ZT14` = NULL)
yeastCPDTimepoints = list(`5min` = NULL, `20min` = NULL, `1h` = NULL)
GM12878CisplatinTimepoints = list(`90min` = NULL)
CSBCPDTimepoints = list(`1h` = NULL)
XPCCPDTimepoints = list(`1h` = NULL)

@@

NHF1DataDirectory = file.path(deaminationDataDirectory, "NHF1")
NHF1SequenceAndPositionDataDirectory = file.path(NHF1DataDirectory, "sequence_and_position_analysis")
NHF1ExcisionSiteDataDirectory = file.path(NHF1DataDirectory, "excision_site_analysis")
NHF1GeneralReadSequenceDataDirectory = file.path(NHF1DataDirectory, "general_read_sequences")

arabidopsisDataDirectory = file.path(deaminationDataDirectory, "Arabidopsis")
arabidopsisSequenceAndPositionDataDirectory = file.path(arabidopsisDataDirectory, "sequence_and_position_analysis")
arabidopsisExcisionSiteDataDirectory = file.path(arabidopsisDataDirectory, "excision_site_analysis")

yeastDataDirectory = file.path(deaminationDataDirectory, "yeast")
yeastSequenceAndPositionDataDirectory = file.path(yeastDataDirectory, "sequence_and_position_analysis")
yeastExcisionSiteDataDirectory = file.path(yeastDataDirectory, "excision_site_analysis")

GM12878DataDirectory = file.path(deaminationDataDirectory, "GM12878")
GM12878SequenceAndPositionDataDirectory = file.path(GM12878DataDirectory, "sequence_and_position_analysis")

CSBDataDirectory = file.path(deaminationDataDirectory, "CS-B")
CSBSequenceAndPositionDataDirectory = file.path(CSBDataDirectory, "sequence_and_position_analysis")

XPCDataDirectory = file.path(deaminationDataDirectory, "XP-C")
XPCSequenceAndPositionDataDirectory = file.path(XPCDataDirectory, "sequence_and_position_analysis")
```

@@

```{r read_figure_2_data}
NHF1CPDMismatchDataAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllReps)) {
  NHF1CPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDMismatchDataAllReps)[i]
  ))
}
```

@@

plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                         title = "NHF1 CPD 1h All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps Mismatch Pos Frequencies")
```

```{r read_figure_3_data}
NHF1CPDMMFreqZScoresAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMMFreqZScoresAllReps)) {
  NHF1CPDMMFreqZScoresAllReps[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDMMFreqZScoresAllReps)[i], includedMismatches = c("C>T")
  ))
}

@@

NHF1CPDTGGSeqFreqAllReps = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDTGGSeqFreqAllReps)) {
  NHF1CPDTGGSeqFreqAllReps[[i]] = fread(generateFilePath(
    directory = NHF1GeneralReadSequenceDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1CPDTGGSeqFreqAllReps)[i], sequence = "TGG"
  ))
}
```

```{r figure_3}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)

@@

plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        expansionOffset = 10, showThreePrimeCutSite = TRUE,
                        showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
# 
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
# 
# plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
#                         expansionOffset = 10, showThreePrimeCutSite = TRUE,
#                         showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
```

```{r read_figure_5_data}
NHF1CPDMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMismatchDataAllRepsFiltered)) {
  NHF1CPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", timepoint = names(NHF1CPDMismatchDataAllRepsFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

NHF1CPDMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDMMFreqZScoresAllRepsFiltered)) {
  NHF1CPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(NHF1CPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
  ))
}

NHF1CPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(NHF1CPDGroupedStatsAllRepsFiltered)) {
  NHF1CPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(NHF1CPDGroupedStatsAllRepsFiltered)[i]
  ))
}

arabidopsisCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(arabidopsisCPDGroupedStatsAllRepsFiltered)) {
  arabidopsisCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(arabidopsisCPDGroupedStatsAllRepsFiltered)[i]
  ))
}

yeastCPDGroupedStatsAllRepsFiltered = list(three_prime = NULL, five_prime = NULL)
for (i in seq_along(yeastCPDGroupedStatsAllRepsFiltered)) {
  yeastCPDGroupedStatsAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastSequenceAndPositionDataDirectory, dataTypeStrings$mismatchPositionStats, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    strandPolarity = names(yeastCPDGroupedStatsAllRepsFiltered)[i]
  ))
}
```

```{r figure_5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)

plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(24:30))

plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         yeastCPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:25))

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
# 
# plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime,
#                          NHF1CPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(22:30))
# 
# plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime,
#                          arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(24:30))
# 
# plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime,
#                          yeastCPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(22:25))

```

```{r read_figure_6_data}
NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
))

NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "three_prime", anchored = TRUE, filtering = "TGG_filtered"
))

NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1ExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    timepoint = names(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

```

```{r figure_6}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 12)

plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 13, maxReadLength = 25)

plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 13, maxReadLength = 25)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
# 
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
# 
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
```

```{r read_figure_8_data}
NHF1CPDCCtoTTMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)) {
  NHF1CPDCCtoTTMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "CC>TT",
    timepoint = names(NHF1CPDCCtoTTMismatchDataAllRepsFiltered)[i]
  ))
}

NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)) {
  NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "CC>TT",
    timepoint = names(NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)[i]
  ))
}

NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "GG>AA",
    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
  ))
}

NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)) {
  NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    directory = NHF1SequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "GG>AA",
    timepoint = names(NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)[i]
  ))
}
```

```{r figure_8}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD 1h All Reps CC>TT Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)

plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD 1h All Reps GG>AA Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDCCtoTTMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps CC>TT Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDCCtoTTMMFreqZScoresAllRepsFiltered)
# 
# plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered,
#                                          title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered)
```

```{r read_figure_S1_data}
NHF1SixFourMismatchDataAllReps = NHF1SixFourTimepoints
for (i in seq_along(NHF1SixFourMismatchDataAllReps)) {
  NHF1SixFourMismatchDataAllReps[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "6-4", repitition = "all_reps",
    timepoint = names(NHF1SixFourMismatchDataAllReps)[i]
  ))
}

GM12878CisplatinMismatchDataAllReps = GM12878CisplatinTimepoints
for (i in seq_along(GM12878CisplatinMismatchDataAllReps)) {
  GM12878CisplatinMismatchDataAllReps[[i]] = fread(generateFilePath(
    GM12878SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "GM12878", lesion = "cisplatin", repitition = "all_reps",
    timepoint = names(GM12878CisplatinMismatchDataAllReps)[i]
  ))
}
```

```{r figure_S1}
plotMismatchTypeFrequencies(NHF1SixFourMismatchDataAllReps$`20min`,
                            title = "NHF1 6-4 20min All Reps Mismatch Type Frequencies")

plotTrinucleotideContext(NHF1SixFourMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
                         title = "NHF1 6-4 20min All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(NHF1SixFourMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
                                title = "NHF1 6-4 20min All Reps Mismatch Pos Frequencies")

plotMismatchTypeFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`,
                            title = "GM12878 Cisplatin 90min All Reps Mismatch Type Frequencies")

plotTrinucleotideContext(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
                         title = "GM12878 Cisplatin 90min All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(GM12878CisplatinMismatchDataAllReps$`90min`, includedTypes = c("C>T"),
                                title = "GM12878 Cisplatin 90min All Reps Mismatch Pos Frequencies")
```

```{r read_figure_S2_data}
arabidopsisCPDMismatchDataAllReps = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisCPDMismatchDataAllReps)) {
  arabidopsisCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
    timepoint = names(arabidopsisCPDMismatchDataAllReps)[i]
  ))
}

yeastCPDMismatchDataAllReps = yeastCPDTimepoints
for (i in seq_along(yeastCPDMismatchDataAllReps)) {
  yeastCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    yeastSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
    timepoint = names(yeastCPDMismatchDataAllReps)[i]
  ))
}

CSBCPDMismatchDataAllReps = CSBCPDTimepoints
for (i in seq_along(CSBCPDMismatchDataAllReps)) {
  CSBCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    CSBSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "CS-B", lesion = "CPD", repitition = "all_reps",
    timepoint = names(CSBCPDMismatchDataAllReps)[i]
  ))
}

XPCCPDMismatchDataAllReps = XPCCPDTimepoints
for (i in seq_along(XPCCPDMismatchDataAllReps)) {
  XPCCPDMismatchDataAllReps[[i]] = fread(generateFilePath(
    XPCSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "XP-C", lesion = "CPD", repitition = "all_reps",
    timepoint = names(XPCCPDMismatchDataAllReps)[i]
  ))
}
```

```{r figure_S2}
plotMismatchTypeFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2,
                            title = "Arabidopsis CPD ZT2 All Reps Mismatch Type Frequencies")

plotTrinucleotideContext(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
                         title = "Arabidopsis CPD ZT2 All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(arabidopsisCPDMismatchDataAllReps$ZT2, includedTypes = c("C>T"),
                                title = "Arabidopsis CPD ZT2 All Reps Mismatch Pos Frequencies")

plotMismatchTypeFrequencies(yeastCPDMismatchDataAllReps$`20min`,
                            title = "Yeast CPD 20min All Reps Mismatch Type Frequencies")

plotTrinucleotideContext(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
                         title = "Yeast CPD 20min All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(yeastCPDMismatchDataAllReps$`20min`, includedTypes = c("C>T"),
                                title = "Yeast CPD 20min All Reps Mismatch Pos Frequencies")

plotMismatchTypeFrequencies(CSBCPDMismatchDataAllReps$`1h`,
                            title = "CS-B CPD 1h All Reps Mismatch Type Frequencies")

plotTrinucleotideContext(CSBCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                         title = "CS-B CPD 1h All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(CSBCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                title = "CS-B CPD 1h All Reps Mismatch Pos Frequencies")

plotMismatchTypeFrequencies(XPCCPDMismatchDataAllReps$`1h`,
                            title = "XP-C CPD 1h All Reps Mismatch Type Frequencies")

plotTrinucleotideContext(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                         title = "XP-C CPD 1h All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(XPCCPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                title = "XP-C CPD 1h All Reps Mismatch Pos Frequencies")
```

```{r read_figure_S3_data}
arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps",
    timepoint = names(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}

yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)) {
  yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered[[i]] = fread(generateFilePath(
    yeastExcisionSiteDataDirectory, dataTypeStrings$sequenceFrequency, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps",
    timepoint = names(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered)[i],
    strandPolarity = "three_prime", anchored = TRUE, sequence = "YR", filtering = "TGG_filtered"
  ))
}
```

```{r figure_S3}
plotSequenceFrequencies(arabidopsisThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$ZT2,
                        title = "Arabidopsis CPD ZT2 All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 15, maxReadLength = 25)

plotSequenceFrequencies(yeastThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`20min`,
                        title = "Yeast CPD 20min All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 11, maxReadLength = 19)
```
